---
title: "ego_ignorance"
author: "S. Shin"
date: '2022-10-28'
output: html_document
---

# Load packages
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(tidyr)
library(AICcmodavg)
library(broom.mixed)
library(nnet)
library(lme4)
library(emmeans)
library(effectsize)
library(pwr)
library(tidyverse)
```

#Pilot

##Load Data
```{r}
df.pilot.trials <- read_csv("../../data/pilot/ego_ignorance_thesis-trials.csv")
```

##Wrangle Data
```{r}
#quick function to count occluders in a string
n_occluders <- Vectorize(function(x) {
  return(sum(as.numeric(strsplit(x, '')[[1]])))
})

#add some info
df.pilot.trials <- df.pilot.trials %>% 
  filter(workerid != 32) %>% #worker 32 timed out on prolific. Their submission is excluded
  mutate(
    response_alter_occluded = case_when(
      substring(alter_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    response_ego_occluded = case_when(
      substring(ego_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    num_ego_occluders = n_occluders(ego_occluders),
    num_alter_occluders = n_occluders(alter_occluders),
    response_ball_position = (response==ball_pos),
    experiment = 'Pilot'
  ) 
```

##Get Demographics
```{r}
#get demos
df.pilot.demos <- read_csv("../../data/pilot/ego_ignorance_thesis-participants.csv") 

pilot.demos.gender <- df.pilot.demos %>% 
  count(gender)
pilot.demos.gender
pilot.mean_age <- mean(df.pilot.demos$age)
pilot.mean_age
```

##Figures

###Interest in Alter Knowledge (violin)
```{r}

alter_ig_data_pilot_occluders <- df.pilot.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  mutate(
    ego_can_infer = case_when(ego_can_infer~'Knowledge', TRUE~'Ignorance'),
    response_alter_occluded = case_when(response_alter_occluded~"Occluded", TRUE~'Visible'),
    num_alter_visible = 3 - num_alter_occluders
  ) %>% 
  group_by(ego_can_infer, workerid) %>% 
  summarize(
    total_alt_occluded = sum(num_alter_occluders),
    total_not_occluded = sum(num_alter_visible)
    ) 

alter_ig_data_pilot <- df.pilot.trials %>%
  filter(
    !ego_ball_visible
  ) %>% 
  mutate(
    ego_can_infer = case_when(ego_can_infer~'Knowledge', TRUE~'Ignorance'),
    response_alter_occluded = case_when(response_alter_occluded~"Occluded", TRUE~'Visible'),
  ) %>% 
  group_by(ego_can_infer, response_alter_occluded, workerid) %>% 
  summarize(
    responses = n()
  ) %>% 
  inner_join(alter_ig_data_pilot_occluders) %>% 
  mutate(
    proportional_responses = case_when(
      response_alter_occluded == 'Occluded' ~ responses / total_alt_occluded,
      response_alter_occluded == 'Visible' ~ responses / total_not_occluded
    )
  )



#calculate means 
pilot_fig_means <- alter_ig_data_pilot  %>% 
  group_by(ego_can_infer, response_alter_occluded) %>% 
  dplyr::summarize(mean = mean(proportional_responses))


fig0 <- ggplot(
  data = alter_ig_data_pilot,
  mapping = aes(
    x = response_alter_occluded,
    y = proportional_responses,
    color = response_alter_occluded)
  ) +
  geom_point(
    position = position_jitterdodge(dodge.width = 0.9, jitter.width = 0.2),
    size = 0.9,
    alpha = 1) +
  geom_violin(
    aes(alpha = 0),
    position = position_dodge(width=0.9)) +
  geom_boxplot(
    aes(alpha = 0),
    outlier.shape = NA,
    width = 0.15,
    position = position_dodge(width=0.9),
    fatten = NULL) +
  geom_line(
    data = pilot_fig_means,
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=ego_can_infer),
    color="grey30"
    ) +
  geom_point(
    data = pilot_fig_means, 
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=response_alter_occluded),
    position = position_dodge(width=0.9)
  ) + 
  facet_grid(~ego_can_infer) +
  xlab(element_blank()) +
  ylab("Percentage Responses") +
  theme_minimal() +
  scale_colour_ptol() +
  theme(
    legend.position = "none",
    strip.text.x = element_text(size = 14),
    axis.title = element_text(size = 14, margin = unit(c(0,0.2,0,0), 'cm')),
    axis.text = element_text(size = 12),)
```

## Analyses

###Interest in alter knowledge (GLM)
```{r}

df.pilot.glm.0 <- df.pilot.trials %>% 
  filter(
    !ego_ball_visible
  )

glm.0 <- glmer(
  formula = response_alter_occluded ~ ego_can_infer + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = df.pilot.glm.0,
  family = 'binomial')

glm.1 <- glmer(
  formula = response_alter_occluded ~ 1 + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = df.pilot.glm.0,
  family = 'binomial')

aov.0 <- anova(glm.0, glm.1)
aov.0
```

####Pairwise follow-up
```{r}
#get participant level summary
emmeans(glm.0, pairwise ~ ego_can_infer)
```

####Post-hoc power analysis
```{r}
#find participant level probabilities of selecting an alter occluded position when !ego_ball_visible
#This corrects for a baseline differrence in the number of occluded, as compared to non-occluded positions. This baseline difference exists in the pilot but not the other experiments
pilot_alter_ig_data <- df.pilot.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  group_by(ego_can_infer, response_alter_occluded, workerid) %>% 
  summarize(
    responses = n(),
    total_alt_occluded = sum(num_alter_occluders)
  )
pilot_corrected_alter_ig_data <- pilot_alter_ig_data %>% 
  group_by(ego_can_infer, workerid) %>% 
  summarize(
    total_condition_alt_occluded = sum(total_alt_occluded)) %>% 
  inner_join(pilot_alter_ig_data, by = c('ego_can_infer', 'workerid')) %>% 
  filter(response_alter_occluded) %>% 
  mutate(
    probability_response_alter_occluded = responses / total_condition_alt_occluded
  )

#Are participants more likely to select alter occluded positions when they know where the ball is? (and therefore more likely to select alter-visible positions when they don't know where the ball is)
#performed on participant x condition 'probability score' (total number of occluded or non-occluded positions corrected for the baseline frequency of occluded or non-occluded positions)
aov.1.pwr <- aov(probability_response_alter_occluded ~ ego_can_infer + workerid, data = pilot_corrected_alter_ig_data)

#cohens-f = 0.27 for affect of ego_can_infer
cohens_f(aov.1.pwr)

#power analysis based upon f=0.27, power=0.8, 
pwr.anova.test(k=2,            # 2 groups are compared
               f=.27,          # effect size due to ego_can_infer
               sig.level=.05,  # alpha/sig. level = .05
               power = 0.8)       # confint./power = .8
#shows n=55
```

#EXPERIMENT 1a

##Load Data
```{r}
df.ex1.trials <- read_csv("../../data/experiment_1a/ego_ignorance_thesis_experiment_1-trials.csv")
```

##Wrangle Data
```{r}
#quick function to count occluders in a string
n_occluders <- Vectorize(function(x) {
  return(sum(as.numeric(strsplit(x, '')[[1]])))
})

#add some info
df.ex1.trials <- df.ex1.trials %>% 
  mutate(
    response_alter_occluded = case_when(
      substring(alter_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    response_ego_occluded = case_when(
      substring(ego_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    num_ego_occluders = n_occluders(ego_occluders),
    num_alter_occluders = n_occluders(alter_occluders),
    response_ball_position = (response==ball_pos),
    experiment = 'Experiment 1')

```

##Get Demographics
```{r}
#get demos
df.ex1.demos <- read_csv("../../data/experiment_1a/ego_ignorance_thesis_experiment_1-participants.csv") 

ex1.demos.gender <- df.ex1.demos %>% 
  count(gender)
ex1.demos.gender
ex1.mean_age <- mean(df.ex1.demos$age)
ex1.mean_age
```

##Figures

###Interest in Alter Knowledge (violin)
```{r}
alter_ig_ex1_data <- df.ex1.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  mutate(
    ego_can_infer = case_when(ego_can_infer~'Knowledge', TRUE~'Ignorance'),
    response_alter_occluded = case_when(response_alter_occluded~"Occluded", TRUE~'Visible')
  ) %>% 
  count(ego_can_infer, response_alter_occluded, workerid)

#quickly get the number of total responses in each category
ex1_total_responses <- alter_ig_ex1_data %>% 
  group_by(workerid, ego_can_infer) %>% 
  mutate(total_responses = sum(n))

#convert responses to percentages
alter_ig_ex1_data <- alter_ig_ex1_data %>% 
  inner_join(ex1_total_responses) %>% 
  mutate(percentage = (n / total_responses)*100)

#calculate means 
ex1_fig_means <- alter_ig_ex1_data %>% 
  group_by(ego_can_infer, response_alter_occluded) %>% 
  dplyr::summarize(mean = mean(percentage))

fig1_char <- ggplot(
  data = alter_ig_ex1_data,
  mapping = aes(
    x = response_alter_occluded,
    y = percentage,
    color = response_alter_occluded)
  ) +
  geom_point(
    position = position_jitterdodge(dodge.width = 0.9, jitter.width = 0.2),
    size = 0.9,
    alpha = 1) +
  geom_violin(
    aes(alpha = 0),
    position = position_dodge(width=0.9)) +
  geom_boxplot(
    aes(alpha = 0),
    outlier.shape = NA,
    width = 0.15,
    position = position_dodge(width=0.9),
    fatten = NULL) +
  geom_line(
    data = ex1_fig_means,
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=ego_can_infer),
    color="grey30"
    ) +
  geom_point(
    data = ex1_fig_means, 
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=response_alter_occluded),
    position = position_dodge(width=0.9)
  ) + 
  facet_grid(~ego_can_infer) +
  xlab(element_blank()) +
  ylab("Participant Responses (percent)") +
  ylim(0, 100) +
  theme_minimal() +
  scale_colour_ptol() +
  theme(
    legend.position = "none",
    strip.text.x = element_text(size = 14),
    axis.title = element_text(size = 14, margin = unit(c(0,0.2,0,0), 'cm')),
    axis.text = element_text(size = 12),)

fig1_char
```

##Analyses

###Interest in alter knowledge from responses (GLM)
```{r}

ex1_alter_ig_data <- df.ex1.trials %>% 
  filter(
    !ego_ball_visible
  )

glm.2 <- glmer(
  formula = response_alter_occluded ~ ego_can_infer + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex1_alter_ig_data,
  family = 'binomial')

glm.3 <- glmer(
  formula = response_alter_occluded ~ 1 + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex1_alter_ig_data,
  family = 'binomial')

aov.1 <- anova(glm.2, glm.3)

#show results
aov.1

#show number of trials per participant
n_trials.ex1 <- df.ex1.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  count(workerid) %>% 
  summarise(avg_trials = mean(n))
n_trials.ex1
```

####Follow-up
```{r}
emmeans(glm.2, pairwise ~ ego_can_infer)
```

# EXPERIMENT 1b (replication)

##load data
```{r}
#get ids of completed participants
df.ex1_rep.trials <- read_csv("../../data/experiment_1b/ex1_rep_trials.csv")
df.ex1_rep.participants <- read_csv("../../data/experiment_1b/ex1_rep_participants.csv") %>% 
  filter(!is.na(gender))

```

## Wrangle Data
```{r}
#quick function to count occluders in a string
n_occluders <- Vectorize(function(x) {
  return(sum(as.numeric(strsplit(x, '')[[1]])))
})

#add some info
df.ex1_rep.trials <- df.ex1_rep.trials %>% 
  mutate(
    accuracy = as.logical(accuracy),
    character_choice = as.integer(character_choice),
    ego_can_infer = as.logical(ego_can_infer),
    ego_ball_visible = as.logical(ego_ball_visible),
    response = as.integer(response),
    response_alter_occluded = case_when(
      substring(alter_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    response_ego_occluded = case_when(
      substring(ego_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    num_ego_occluders = n_occluders(ego_occluders),
    num_alter_occluders = n_occluders(alter_occluders),
    response_ball_position = (response==ball_pos))
```

##Get Demographics
```{r}
#get demos
df.ex1_rep.demos <- read_csv("../../data/experiment_1b/ex1_rep_participants.csv") %>% 
  filter(workerid %in% df.ex1_rep.trials$workerid)

ex1_rep.demos.gender <- df.ex1_rep.demos %>% 
  count(gender)
ex1_rep.demos.gender
ex1_rep.mean_age <- mean(df.ex1_rep.demos$age)
ex1_rep.mean_age
```

##Analyses

### Accuracy in 'easy' trials
```{r}
easy_trials.ex1_rep <- df.ex1_rep.trials %>% 
  filter(ego_can_infer & alter_can_infer) %>% 
  group_by(workerid) %>% 
  summarise(accuracy = mean(accuracy_bool)) %>% 
  ungroup() %>% 
  summarize(mean = mean(accuracy), sd = sd(accuracy))

easy_trials.ex1_rep
```

###Interest in alter knowledge from responses (GLM)
```{r}

ex1_rep_alter_ig_data <- df.ex1_rep.trials %>% 
  filter(
    !ego_ball_visible
  )

glm.4 <- glmer(
  formula = response_alter_occluded ~ ego_can_infer + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex1_rep_alter_ig_data,
  family = 'binomial')

glm.5 <- glmer(
  formula = response_alter_occluded ~ 1 + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex1_rep_alter_ig_data,
  family = 'binomial')

aov.2 <- anova(glm.4, glm.5)

aov.2

#show number of trials per participant
n_trials.ex1b <- df.ex1_rep.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  count(workerid) %>% 
  summarise(avg_trials = mean(n))
n_trials.ex1b
```

###Follow-up
```{r}
emmeans(glm.4, pairwise ~ ego_can_infer)
```


## Figures

###Interest in Alter Knowledge (violin)
```{r}
alter_ig_ex1_rep_data <- df.ex1_rep.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  mutate(
    ego_can_infer = case_when(ego_can_infer~'Knowledge', TRUE~'Ignorance'),
    response_alter_occluded = case_when(response_alter_occluded~"Occluded", TRUE~'Visible')
  ) %>% 
  count(ego_can_infer, response_alter_occluded, workerid)

#quickly get the number of total responses in each category
ex1_rep_total_responses <- alter_ig_ex1_rep_data %>% 
  group_by(workerid, ego_can_infer) %>% 
  mutate(total_responses = sum(n))

#convert responses to percentages
alter_ig_ex1_rep_data <- alter_ig_ex1_rep_data %>% 
  inner_join(ex1_rep_total_responses) %>% 
  mutate(percentage = (n / total_responses)*100)

#calculate means 
ex1_rep_fig_means <- alter_ig_ex1_rep_data %>% 
  group_by(ego_can_infer, response_alter_occluded) %>% 
  dplyr::summarize(mean = mean(percentage))

fig1b_char <- ggplot(
  data = alter_ig_ex1_rep_data,
  mapping = aes(
    x = response_alter_occluded,
    y = percentage,
    color = response_alter_occluded)
  ) +
  geom_point(
    position = position_jitterdodge(dodge.width = 0.9, jitter.width = 0.2),
    size = 0.9,
    alpha = 1) +
  geom_violin(
    aes(alpha = 0),
    position = position_dodge(width=0.9)) +
  geom_boxplot(
    aes(alpha = 0),
    outlier.shape = NA,
    width = 0.15,
    position = position_dodge(width=0.9),
    fatten = NULL) +
  geom_line(
    data = ex1_rep_fig_means,
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=ego_can_infer),
    color="grey30"
    ) +
  geom_point(
    data = ex1_rep_fig_means, 
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=response_alter_occluded),
    position = position_dodge(width=0.9)
  ) + 
  facet_grid(~ego_can_infer) +
  xlab(element_blank()) +
  ylab("Participant Responses (percent)") +
  ylim(0, 100) +
  theme_minimal() +
  scale_colour_ptol() +
  theme(
    legend.position = "none",
    strip.text.x = element_text(size = 14),
    axis.title = element_text(size = 14, margin = unit(c(0,0.2,0,0), 'cm')),
    axis.text = element_text(size = 12),)

fig1b_char
```

#EXPERIMENT 2a

##Load Data
```{r}
df.ex2a.trials <- read_csv("../../data/experiment_2a/ego_ignorance_thesis_ex2a-trials.csv")
```

##Wrangle Data
```{r}
#quick function to count occluders in a string
n_occluders <- Vectorize(function(x) {
  return(sum(as.numeric(strsplit(x, '')[[1]])))
})

#add some info
df.ex2a.trials <- df.ex2a.trials %>% 
  mutate(
    response_alter_occluded = case_when(
      substring(alter_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    response_ego_occluded = case_when(
      substring(ego_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    num_ego_occluders = n_occluders(ego_occluders),
    num_alter_occluders = n_occluders(alter_occluders),
    response_ball_position = (response==ball_pos),
    ego_can_infer = case_when(
                            ego_ball_visible ~ TRUE,
                            num_ego_occluders == 1 ~ TRUE,
                            TRUE ~ FALSE),
    collective_can_infer = case_when(
                            ego_can_infer & alter_can_infer ~ TRUE,
                            TRUE ~ FALSE),
    experiment = 'Experiment 2a'
    )
```

##Get Demographics
```{r}
#get demos
df.ex2a.demos <- read_csv("../../data/experiment_2a/ego_ignorance_thesis_ex2a-participants.csv") 

ex2a.demos.gender <- df.ex2a.demos %>% 
  count(gender)
ex2a.demos.gender
ex2a.mean_age <- mean(df.ex2a.demos$age, na.rm=TRUE)
ex2a.mean_age
```

##Figures

###Interest in Alter Knowledge (violin)
```{r}
#get participant level summary (showing total responses)
alter_ig_ex2a_data <- df.ex2a.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  mutate(
    ego_can_infer = case_when(ego_can_infer~'Knowledge', TRUE~'Ignorance'),
    response_alter_occluded = case_when(response_alter_occluded~"Occluded", TRUE~'Visible')
  ) %>% 
  count(ego_can_infer, response_alter_occluded, workerid)

#quickly get the number of total responses in each category
ex2a_total_responses <- alter_ig_ex2a_data %>% 
  group_by(workerid, ego_can_infer) %>% 
  mutate(total_responses = sum(n))

#convert responses to percentages
alter_ig_ex2a_data <- alter_ig_ex2a_data %>% 
  inner_join(ex2a_total_responses) %>% 
  mutate(percentage = (n / total_responses)*100)

#calculate means 
ex2a_fig_means <- alter_ig_ex2a_data %>% 
  group_by(ego_can_infer, response_alter_occluded) %>% 
  dplyr::summarize(mean = mean(percentage))

#make plot
fig1_nochar <- ggplot(
  data = alter_ig_ex2a_data,
  mapping = aes(
    x = response_alter_occluded,
    y = percentage,
    color = response_alter_occluded)
  ) +
  geom_point(
    position = position_jitterdodge(dodge.width = 0.9, jitter.width = 0.2),
    size = 0.9,
    alpha = 1) +
  geom_violin(
    aes(alpha = 0),
    position = position_dodge(width=0.9)) +
  geom_boxplot(
    aes(alpha = 0),
    outlier.shape = NA,
    width = 0.15,
    position = position_dodge(width=0.9),
    fatten = NULL) +
  geom_line(
    data = ex2a_fig_means,
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=ego_can_infer),
    color="grey30"
    ) +
  geom_point(
    data = ex2a_fig_means, 
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=response_alter_occluded),
    position = position_dodge(width=0.9)
  ) + 
  facet_grid(~ego_can_infer) +
  xlab(element_blank()) +
  ylab("Participant Responses (percent)") +
  ylim(0, 100) +
  theme_minimal() +
  scale_colour_ptol() +
  theme(
    legend.position = "none",
    strip.text.x = element_text(size = 14),
    axis.title = element_text(size = 14, margin = unit(c(0,0.2,0,0), 'cm')),
    axis.text = element_text(size = 12),)
```

##Analyses

###Interest in alter knowledge (GLM)
```{r}

ex2a_alter_ig_data <- df.ex2a.trials %>% 
  filter(
    !ego_ball_visible
  )

glm.6 <- glmer(
  formula = response_alter_occluded ~ ego_can_infer + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex2a_alter_ig_data,
  family = 'binomial')

glm.7 <- glmer(
  formula = response_alter_occluded ~ 1 + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex2a_alter_ig_data,
  family = 'binomial')

aov.3 <- anova(glm.6, glm.7)

aov.3

#show number of trials per participant
n_trials.ex2a <- df.ex2a.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  count(workerid) %>% 
  summarise(avg_trials = mean(n))
n_trials.ex2a
```

####Follow-up
```{r}
emmeans(glm.6, pairwise ~ ego_can_infer)
```

#EXPERIMENT 2b

##Load Data
```{r}
df.ex2b.trials <- read_csv("../../data/experiment_2b/ego_ignorance_thesis_experiment_2b-trials.csv")
```

##Wrangle Data
```{r}
#quick function to count occluders in a string
n_occluders <- Vectorize(function(x) {
  return(sum(as.numeric(strsplit(x, '')[[1]])))
})

#add some info
df.ex2b.trials <- df.ex2b.trials %>% 
  mutate(
    response_alter_occluded = case_when(
      substring(alter_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    response_ego_occluded = case_when(
      substring(ego_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    num_ego_occluders = n_occluders(ego_occluders),
    num_alter_occluders = n_occluders(alter_occluders),
    response_ball_position = (response==ball_pos),
    experiment = 'Experiment 2b')
```

##Get Demographics
```{r}
#get demos
df.ex2b.demos <- read_csv("../../data/experiment_2b/ego_ignorance_thesis_experiment_2b-participants.csv") 

ex2b.demos.gender <- df.ex2b.demos %>% 
  count(gender)
ex2b.demos.gender
ex2b.mean_age <- mean(df.ex2b.demos$age)
ex2b.mean_age
```

##Figures

###Interest in Alter Knowledge (violin)
```{r}
alter_ig_ex2b_data <- df.ex2b.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  mutate(
    ego_can_infer = case_when(ego_can_infer~'Knowledge', TRUE~'Ignorance'),
    response_alter_occluded = case_when(response_alter_occluded~"Occluded", TRUE~'Visible')
  ) %>% 
  count(ego_can_infer, response_alter_occluded, workerid)

#quickly get the number of total responses in each category
ex2b_total_responses <- alter_ig_ex2b_data %>% 
  group_by(workerid, ego_can_infer) %>% 
  mutate(total_responses = sum(n))

#convert responses to percentages
alter_ig_ex2b_data <- alter_ig_ex2b_data %>% 
  inner_join(ex2b_total_responses) %>% 
  mutate(percentage = (n / total_responses)*100)

#calculate means 
ex2b_fig_means <- alter_ig_ex2b_data %>% 
  group_by(ego_can_infer, response_alter_occluded) %>% 
  dplyr::summarize(mean = mean(percentage))

fig1_lamp <- ggplot(
  data = alter_ig_ex2b_data,
  mapping = aes(
    x = response_alter_occluded,
    y = percentage,
    color = response_alter_occluded)
  ) +
  geom_point(
    position = position_jitterdodge(dodge.width = 0.9, jitter.width = 0.2),
    size = 0.9,
    alpha = 1) +
  geom_violin(
    aes(alpha = 0),
    position = position_dodge(width=0.9)) +
  geom_boxplot(
    aes(alpha = 0),
    outlier.shape = NA,
    width = 0.15,
    position = position_dodge(width=0.9),
    fatten = NULL) +
  geom_line(
    data = ex2b_fig_means,
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=ego_can_infer),
    color="grey30"
    ) +
  geom_point(
    data = ex2b_fig_means, 
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=response_alter_occluded),
    position = position_dodge(width=0.9)
  ) + 
  facet_grid(~ego_can_infer) +
  xlab(element_blank()) +
  ylab("Participant Responses (percent)") +
  ylim(0,100) +
  theme_minimal() +
  scale_colour_ptol() +
  theme(
    legend.position = "none",
    strip.text.x = element_text(size = 14),
    axis.title = element_text(size = 14, margin = unit(c(0,0.2,0,0), 'cm')),
    axis.text = element_text(size = 12),)
```

##Analyses

###Interest in alter knowledge from responses (GLM)
```{r}

ex2b_alter_ig_data <- df.ex2b.trials %>% 
  filter(
    !ego_ball_visible
  )

glm.8 <- glmer(
  formula = response_alter_occluded ~ ego_can_infer + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex2b_alter_ig_data,
  family = 'binomial')

glm.9 <- glmer(
  formula = response_alter_occluded ~ 1 + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex2b_alter_ig_data,
  family = 'binomial')

aov.4 <- anova(glm.8, glm.9)

aov.4

#show number of trials per participant
n_trials.ex2b <- df.ex2b.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  count(workerid) %>% 
  summarise(avg_trials = mean(n))
n_trials.ex2b
```

####Follow-up
```{r}
emmeans(glm.8, pairwise ~ ego_can_infer)
```

#EXPERIMENT 2c

##Load Data
```{r}
df.ex2c.trials <- read_csv("../../data/experiment_2c/ego_ignorance_thesis_experiment_2c-trials.csv")
```

##Wrangle Data
```{r}
#quick function to count occluders in a string
n_occluders <- Vectorize(function(x) {
  return(sum(as.numeric(strsplit(x, '')[[1]])))
})

#add some info
df.ex2c.trials <- df.ex2c.trials %>% 
  mutate(
    response_alter_occluded = case_when(
      substring(alter_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    response_ego_occluded = case_when(
      substring(ego_occluders, response+1, response+1) == '1' ~ TRUE,
      TRUE ~ FALSE
    ),
    num_ego_occluders = n_occluders(ego_occluders),
    num_alter_occluders = n_occluders(alter_occluders),
    response_ball_position = (response==ball_pos),
    experiment = 'Experiment 2c')
```

##Get Demographics
```{r}
#get demos
df.ex2c.demos <- read_csv("../../data/experiment_2c/ego_ignorance_thesis_experiment_2c-participants.csv") 

ex2c.demos.gender <- df.ex2c.demos %>% 
  count(gender)
ex2c.demos.gender
ex2c.mean_age <- mean(df.ex2c.demos$age)
ex2c.mean_age
```

##Figures

###Interest in Alter Knowledge (violin)
```{r}
alter_ig_ex2c_data <- df.ex2c.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  mutate(
    ego_can_infer = case_when(ego_can_infer~'Knowledge', TRUE~'Ignorance'),
    response_alter_occluded = case_when(response_alter_occluded~"Occluded", TRUE~'Visible')
  ) %>% 
  count(ego_can_infer, response_alter_occluded, workerid)

#quickly get the number of total responses in each category
ex2c_total_responses <- alter_ig_ex2c_data %>% 
  group_by(workerid, ego_can_infer) %>% 
  mutate(total_responses = sum(n))

#convert responses to percentages
alter_ig_ex2c_data <- alter_ig_ex2c_data %>% 
  inner_join(ex2c_total_responses) %>% 
  mutate(percentage = (n / total_responses)*100)

#calculate means 
ex2c_fig_means <- alter_ig_ex2c_data %>% 
  group_by(ego_can_infer, response_alter_occluded) %>% 
  dplyr::summarize(mean = mean(percentage))


fig1_ex2achar <- ggplot(
  data = alter_ig_ex2c_data,
  mapping = aes(
    x = response_alter_occluded,
    y = percentage,
    color = response_alter_occluded)
  ) +
  geom_point(
    position = position_jitterdodge(dodge.width = 0.9, jitter.width = 0.2),
    size = 0.9,
    alpha = 1) +
  geom_violin(
    aes(alpha = 0),
    position = position_dodge(width=0.9)) +
  geom_boxplot(
    aes(alpha = 0),
    outlier.shape = NA,
    width = 0.15,
    position = position_dodge(width=0.9),
    fatten = NULL) +
  geom_line(
    data = ex2c_fig_means,
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=ego_can_infer),
    color="grey30"
    ) +
  geom_point(
    data = ex2c_fig_means, 
    mapping = aes(x = response_alter_occluded, 
      y = mean, 
      group=response_alter_occluded),
    position = position_dodge(width=0.9)
  ) + 
  facet_grid(~ego_can_infer) +
  xlab(element_blank()) +
  ylab("Participant Responses (percent)") +
  ylim(0, 100) +
  theme_minimal() +
  scale_colour_ptol() +
  theme(
    legend.position = "none",
    strip.text.x = element_text(size = 14),
    axis.title = element_text(size = 14, margin = unit(c(0,0.2,0,0), 'cm')),
    axis.text = element_text(size = 12))
```

##Analyses

###Interest in alter knowledge from responses (GLM)
```{r}

ex2c_alter_ig_data <- df.ex2c.trials %>% 
  filter(
    !ego_ball_visible
  )

glm.10 <- glmer(
  formula = response_alter_occluded ~ ego_can_infer + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex2c_alter_ig_data,
  family = 'binomial')

glm.11 <- glmer(
  formula = response_alter_occluded ~ 1 + num_alter_occluders + (ego_can_infer + num_alter_occluders|workerid),  
  data = ex2c_alter_ig_data,
  family = 'binomial')

aov.5 <- anova(glm.10, glm.11)

aov.5

#show number of trials per participant
n_trials.ex2c <- df.ex2c.trials %>% 
  filter(
    !ego_ball_visible
  ) %>% 
  count(workerid) %>% 
  summarise(avg_trials = mean(n))
n_trials.ex2c
```

####Follow-up
```{r}
emmeans(glm.10, pairwise ~ ego_can_infer)
```

# COMBINED FIGURES/ANALYSES

##'Correct' Choices?
```{r}

#overall df
combined_data <- df.pilot.trials %>% 
  rbind(df.ex2a.trials, df.ex1.trials, df.ex2b.trials, df.ex2c.trials) %>% 
  mutate(
    experiment = factor(experiment, levels = c('Pilot', 'Experiment 1', 'Experiment 2a', 'Experiment 2b', 'Experiment 2c'))
  )
#OVERALL ACCURACY
#For Ex1, when both the participant and the character can see or infer the position of the ball, does the participant select this position?
#For Ex2a-2c, when the participant can see or infer the position of the ball, does the participant select this position?
combined_accuracy_data_overall <- combined_data %>% 
  count(accuracy, experiment, workerid) %>% 
  rename(Responses = n) %>% 
  mutate(accuracy = case_when(accuracy ~ 'correct', TRUE ~ 'incorrect')) %>% 
  pivot_wider(names_from = accuracy, values_from = Responses) %>% 
  mutate(Accuracy = correct / (correct + incorrect)) %>% 
  group_by(experiment) %>% 
  summarise(mean = mean(Accuracy, na.rm=TRUE), sd = sd(Accuracy, na.rm=TRUE))
combined_accuracy_data_overall

```

##Combined Results: Violin Grid
```{r}

#Modify individual plots for grid format
fig1_char <- fig1_char + 
  ggtitle("Experiment 1a") +
  theme_stata() +
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.y = element_text(size = 16, margin = margin(t = 0, r = 10, b = 0, l = 0)),
    axis.text.x = element_text(size = 15),
    strip.text.x = element_text(size = 15),
    axis.text.y = element_text(size=14),
    legend.position = 'none',
    text = element_text(family = "serif")) +
  ylim(10, 90)

fig1b_char <- fig1b_char + 
  ggtitle("Experiment 1b") +
  theme_stata() +
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.y = element_text(size = 16, margin = margin(t = 0, r = 10, b = 0, l = 0)),
    axis.text.x = element_text(size = 15),
    strip.text.x = element_text(size = 15),
    axis.text.y = element_text(size=14),
    legend.position = 'none',
    text = element_text(family = "serif")) +
  ylab(element_blank()) +
  ylim(10, 90)

fig1_nochar <- fig1_nochar + 
  ggtitle("Experiment 2a")+
  theme_stata() +
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.y = element_text(size = 16, margin = margin(t = 0, r = 10, b = 0, l = 0)),
    axis.text.x = element_text(size = 15),
    strip.text.x = element_text(size = 15),
    axis.text.y = element_text(size=14),
    legend.position = 'none',
    text = element_text(family = "serif")) +
  ylim(10, 90)

fig1_lamp <- fig1_lamp + 
  ggtitle("Experiment 2b")+
  theme_stata() +
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.y = element_text(size = 16, margin = margin(t = 0, r = 10, b = 0, l = 0)),
    axis.text.x = element_text(size = 15),
    strip.text.x = element_text(size = 15),
    axis.text.y = element_text(size=14),
    legend.position = 'none',
    text = element_text(family = "serif")) +
  ylab(element_blank()) +
  ylim(10, 90)

fig1_ex2achar <- fig1_ex2achar + 
  ggtitle("Experiment 2c")+
  theme_stata() +
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.text.x = element_text(size = 15),
    strip.text.x = element_text(size = 15),
    axis.text.y = element_text(size=14),
    legend.position = 'none',
    text = element_text(family = "serif")) +
  ylab(element_blank()) +
  ylim(10, 90)

#Paste plots together
layout_ex2 <- rbind(c(1,2,3))
layout_ex1 <- rbind(c(1,2))

combined_fig_ex1 <- arrangeGrob(
  fig1_char,
  fig1b_char,
  layout_matrix = layout_ex1
)

combined_fig_ex2 <- arrangeGrob(
  fig1_nochar,
  fig1_lamp,
  fig1_ex2achar,
  layout_matrix = layout_ex2
)

ggsave(filename = "../../figures/combined_fig_ex1.pdf", combined_fig_ex1,
       width = 10,
       height = 5)

ggsave(filename = "../../figures/combined_fig_ex2.pdf", combined_fig_ex2,
       width = 13,
       height = 4.2)
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
